% $Id: Note_ResFit_Main.tex,v 1.17 2010/10/31 18:51:15 mschrode Exp $

% =====  HEADER  ========================================

% ----- Document ----------------------------------------
\documentclass[a4paper]{cmspaper} %USE for CMS machines


% ----- User defined commands ---------------------------
\input{definitions.tex}

% ----- Additional packages -----------------------------
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{multirow}


% ----- pdflatex setup ----------------------------------
\usepackage[pdftex]{color,graphicx}
\usepackage[pdftex]{hyperref}
\hypersetup{unicode=true}
\hypersetup{bookmarks=true}
\hypersetup{pdftitle={Measurement of the Jet pt Response Function in QCD Dijet
    Events using an Unbinned Maximum Likelihood Method}}
\hypersetup{pdfauthor={Matthias Schr\"oder}}
\hypersetup{colorlinks=true}



% =====  DOCUMENT  ======================================

\begin{document}


% ----- Title page and TOC ------------------------------
\begin{titlepage}
  \date{\today}
  \title{Measurement of the Jet $p_{\text{T}}$ Response Function in QCD Dijet
    Events using an Unbinned Maximum Likelihood Method}
  \begin{abstract}
    The analysis of jet final states is an important technique to investigate
    Standard Model and beyond processes and requires a precise
    knowledge of the jet transverse momentum, $p_{\text{T}}$, resolution.	
    A method to determine the resolution from QCD dijet
    events is presented using an unbinned maximum
    likelihood fit of the $p_{\text{T}}$ asymmetry and taking into account the jet $p_{\text{T}}$ spectrum.
    In this way, the determination of the full response function including non-Gaussian
    tails and correction for selection biases is possible.
    Dijet events have a large cross section and hence provide a
    high $p_{\text{T}}$ reach and an early sensitivity to tails.
    So far, a measurement of the Gaussian response has been performed
    on a sample of Collider data corresponding to an integrated luminosity of $2.2\;\text{pb}^{-1}$.
  \end{abstract}
\end{titlepage}
\tableofcontents


% ----- Main part from external files -------------------
\include{Note_ResFit_Introduction}
\include{Note_ResFit_Technique}
\include{Note_ResFit_EventSelection}
\include{Note_ResFit_DataDriven}
\include{Note_ResFit_Systematics}
\include{Note_ResFit_Resolution}
\include{Note_ResFit_Appendix}



% ----- Bibliography ------------------------------------

\begin{thebibliography}{9}
\bibitem{bib:ra2} The CMS SUSY RA2 Group,
  \textit{Inclusive search for SUSY at CMS with the jets plus missing
    momentum signature},
  CMS AN~2010/260 (2010).
\bibitem{bib:asym} C.~Dragoiu \etal,
  \textit{Measurement of the Jet Energy Resolution in $\sqrt{s}=7\tev$
    Collision Data with the Asymmetry Method},
  CMS AN~2010/134 (2010).
\bibitem{bib:cmspas:trigger} The CMS Collaboration,
  \textit{Jet Energy Correction determination at
    \mbox{$\sqrt{s}=7\tev$}},
  CMS PAS JME-10-010
\bibitem{bib:cmspas:monster} The CMS Collaboration,
  \textit{Transverse Momentum and Pseudorapidity Distributions of
    Charged Hadrons in $pp$ Collisions at \mbox{$\sqrt{s} = 0.9$} and $2.36\tev$}, JHEP 02 (2010) 041,
 xarXiv:1002.0621. doi:10.1007/JHEP02(2010)041.
\bibitem{bib:cmspas:vertex} The CMS Collaboration,
  \textit{Tracking and Primary Vertex Results in First $7\tev$ Collisions},
  CMS PAS TRK-10-005 (2010).
\bibitem{bib:pythia} T.~Sj\"ostrand \etal,
  \textit{PYTHIA 6.4 physics and manual},
  JHEP05(2006)026. doi:10.1088/1126-6708/2006/05/026.
\bibitem{bib:geant} GEANT4 Collaboration,
  \textit{GEANT4: A simulation toolkit},
  Nucl. Instrum. and Methods A506 (2003) 250-303. doi:10.1016/S0168-9002(03)01368-8.
\bibitem{bib:akj} M.~Cacciari, G.~P.~Salam, and G.~Soyez,
  \textit{The anti-kt jet clustering algorithm},
  JHEP~0804:063 (2008).
\bibitem{bib:cmspas:jec} The CMS Collaboration,
  \textit{Plans for Jet Energy Corrections at CMS},
  CMS PAS JME-07-002 (2007).
\bibitem{bib:cmspas:jetid}  The CMS Collaboration,
  \textit{Calorimeter Jet Quality Criteria for the First CMS Collision Data},
  CMS PAS JME-09-008 (2008).
%  CMS AN 2010/121 (2010).
\end{thebibliography}



\end{document}
